Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden, England and Wales

### 2020-08-27 reports/article.Rmd
Relative survival. Fix #57.

It should be noted that the risk model does not study THA as an observed intervention. We merely followed the cohort who already had THA. Deaths within 90 days might occur for those patients regardless if THA is inserted or not. The proximity in time however, the maximum of 90 days from THA to death, is an indication that the operation might be the main cause of death for the majority of deceased patients.

>>>>

It should be noted that the risk model does not study THA as an observed intervention. We merely followed the cohort who already had THA. Deaths within 90 days might occur for those patients regardless if THA is inserted or not. The proximity in time however, the maximum of 90 days from THA to death, is an indication that the operation might be the main cause of death for the majority of deceased patients. ~~This was also indicated by a stydy performed by Cnudde et al. who showed that the relative survival for Swedish patients with THA was above 100 % within a year after surgery. Hence, patients with elective THA live longer on average compared to the general population of the same age, sex, and year of birth. An elevated risk of death (a relative survival below 100 %) was seen, however, for Swedish patients with cemented THA during the first 90 days after surgery, indicating that this event is in itself associated with those deaths.[@Cnudde2018b]~~
